Backbone-Store: An API for Automating Local Caching of Web Application Data

### 2012-05-20 paper/paper.tex
Added conclusion to paper

>>>>

\section{Conclusion}

This report described our extension for the Backbone.js library, which
simplifies the task of persisting a collection of data models to a web
browser's local storage, in order to facilitate faster load times and reduced
server load. This extension provides an API to facilitate saving and loading
collections on demand, using one of two different persistence strategies. We
tested our extension using three different demo applications, with different
characteristics for the data that is being used by the application. Our tests
varied both the number of data items in a single collection and the size of
each data itme, to simulate a number of different application scenarios. Our
tests showed that our extension is effective at reducing the load times in many
different scenarios, resulting in an improved experience for the application
user.
